Make any stupid plot you want

### 2020-09-24 draft/intro.tex
I don't even know

\subsection{What is the artist}
\begin{equation}
A: D \mapsto CW\\
\end{equation}

@@

ggplot - strictly hierarchal components (layers), matplotlib - transforms that mostly happen indepently 
"designing and producing statistical graphics is not an art" - ties in w/ difference between drawing program and visualization library, preservation of properties of measurement type and observation type

\cite{wickhamGgplot2ElegantGraphics2016}

>>>>

Wilkenson formulates plotting in terms of varsets, which are sets of variables where variables are:
\begin{equation}
V:O\mapsto V    
\end{equation}
Wilkenson's data algebra is equivalent to data reshapes and join and therefore \cite{wickhamLayeredGrammarGraphics2010,wilkinsonGrammarGraphics2005}

\subsection{What is the artist}
Visualization is a two step process where the artists $A$ transforms the data into visual encodings $V$ and then the renderer $R$ transfroms the encodings $V$ to the set of pixels in $P$.
\begin{equation}
    \label{eq:artist}
    A: D \mapsto V
\end{equation}

\begin{equation}
    \label{eg:renderer}
    R: V \mapsto P
\end{equation}

@@

ggplot - strictly hierarchal components (layers), matplotlib - transforms that mostly happen indepently 
"designing and producing statistical graphics is not an art" - ties in w/ difference between drawing program and visualization library, preservation of properties of measurement type and observation type \cite{wickhamGgplot2ElegantGraphics2016}
